---
title: "MATH4753F25EthanM"
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{MATH4753F25EthanM}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753F25EthanM)
data("DDT.csv")
```

# Description

The MATH4753F25EthanM package includes four functions: myhyper(), myread(), pareto(), and myfirstfunction()
It also includes dataset DDT.  

This vignette demonstrates how to load the dataset and use the functions.

# Load the data set

```{r}
data("DDT")
```


# Using myhyper

This function runs hypergeometirc simulations based on given parameters
```{r}
myhyper(iter=1000,n=19, N=20,r=12)
```

# Using myread

This function reads in csv files
```{r}
ddt <- myread(system.file("extdata", "DDT.csv", package = "MATH4753F25EthanM"))
head(ddt)
```

# Using pareto

This function creates a pareto barplot from a vector
```{r}
freq <- c(15,8,63,20)
RL <- c("None","Both","LegsO","WheelsO")
l <- rep(RL, freq)

pareto(l)
```

# Using myfirstfunction

This function gives a y value that is x squared and creates a graph and table.
```{r}
myfirstfunction(1:4)
```

